Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-14 doc/JFLA2022/paper.tex
fix two formulations in final sections

We believe the \Hydras electronic book has found an attractive set of tradeoffs between the properties of executable books and traditional books. Specifically, in an executable book, the proof assistant language places limits on the structure. For example, Coq may not permit repeating a definition from another module verbatim, since the definition uses section variables that are not present in the current context. Thanks to our \alectr based toolchain, the \Hydras book can include ``live'' code fragments at any point in the text. And in contrast to traditional textbooks, we validate the consistency of code fragments during every build of the electronic book. On the one hand, we follow executable books in providing ``continuous delivery'' of new revisions at a high pace. But on the other hand, we also aim to make regular timestamped versions compatible with specific versions of Coq, akin to new editions of traditional books.

@@

\Hydras wants to provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it can give a concrete view of the mathematical content, not only through full proofs, but also through illuminating computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which  may be also used to experiment new techniques of continuous maintenance of the code and its documentation.

>>>>

We believe the \Hydras electronic book has found an attractive set of tradeoffs between the properties of executable books and traditional books. Specifically, in an executable book, the proof assistant language places limits on the structure. For example, Coq may not permit repeating a definition from another file verbatim, since the definition uses variables that are not present in the current context. Thanks to our \alectr based toolchain, the \Hydras book can include ``live'' code fragments at any point in the text. And in contrast to traditional books, we validate the consistency of code fragments during every build of the electronic book. On the one hand, we follow executable books in providing ``continuous delivery'' of new revisions at a high pace. But on the other hand, we also aim to make regular timestamped versions compatible with specific versions of Coq, akin to new editions of traditional books.

@@

\Hydras wants to provide a connection between scientific literature (\emph{e.g.},~\cite{KP82, KS81, schutte}) and proof assistant technology. For the mathematician, it can give a concrete view of the mathematical content, not only through full proofs, but also through illuminating computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50,000 LOC), dependent on various tools and libraries of the \coq ecosystem, which may be also used to experiment with new maintenance techniques of the code and its documentation.
